---
title: "pkgcheck-editor-extra"
output:
  md_document:
    variant: gfm

  rmarkdown::html_vignette:
    self_contained: no
---

# pkgcheck-editor-extra

<!-- badges: start -->
[![R build status](https://github.com/ropensci-review-tools/pkgcheck-editor-extra/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci-review-tools/pkgcheck-editor-extra/actions?query=workflow%3AR-CMD-check)
[![codecov](https://codecov.io/gh/ropensci-review-tools/pkgcheck-editor-extra/branch/main/graph/badge.svg)](https://codecov.io/gh/ropensci-review-tools/pkgcheck-editor-extra)
[![Project Status: Active](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

Check whether a package is ready for submission to
[rOpenSci](https://ropensci.org)'s peer review system. The primary function
collates the output of
[`goodpractice`](https://github.com/ropensci-review-tools/goodpractice), including `R CMD
check` results, a number of statistics via the [`pkgstats`
package](https://github.com/ropensci-review-tools/pkgstats), and checks for
package structure expected for rOpenSci submissions. The output of this
function immediately indicates whether or not a package is "Ready to Submit".


## Installation

The easiest way to install this package is via the [associated
`r-universe`](https://ropensci-review-tools.r-universe.dev/ui#builds). As
shown there, simply enable the universe with

```{r options, eval = FALSE}
options (repos = c (
    ropenscireviewtools = "https://ropensci-review-tools.r-universe.dev",
    CRAN = "https://cloud.r-project.org"
))
```

And then install the usual way with,

```{r install, eval = FALSE}
install.packages ("pkgcheckEditorExtra")
```

Alternatively, the package can be installed by first installing either the
[remotes](https://remotes.r-lib.org) or [pak](https://pak.r-lib.org/) packages
and running one of the following lines:


```{r remotes, eval = FALSE}
remotes::install_github ("ropensci-review-tools/pkgcheck-editor-extra")
pak::pkg_install ("ropensci-review-tools/pkgcheck-editor-extra")
```

The package can then loaded for use with

```{r library, eval = FALSE}
library (pkgcheckEditorExtra)
```


## Code of Conduct

Please note that this package is released with a [Contributor Code of
Conduct](https://ropensci.org/code-of-conduct/). By contributing to this
project, you agree to abide by its terms.
